---
title: "R-Bootcamp Exercises"
author: "Bernardo Freire Barboza da Cruz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    pdf_document:
        fig_caption: yes
        highlight: pygments
        keep_tex: yes
        number_sections: yes
        toc: yes
        fig_width: 16
        fig_height: 9
        df_print: kable
---

```{r setup, include = FALSE, echo = TRUE}

# To set global options that apply to every chunk in your file, call knitr::opts_chunk$set in a code chunk. 
# Knitr will treat each option that you pass to knitr::opts_chunk$set as a global default that can be overwritten in individual chunk headers.
knitr::opts_chunk$set(
	echo = FALSE, # prevents code, but not the results from appearing in the finished file. This is a useful way to embed figures.
	message = FALSE, # prevents messages that are generated by code from appearing in the finished file.
	warning = FALSE, # prevents warnings that are generated by code from appearing in the finished.
	include = FALSE, # prevents code and results from appearing in the finished file. R Markdown still runs the code in the chunk, and the results can be used by other chunks.
    fig.cap = "<...ADD SOMETHING...>", # adds a caption to graphical results.
    cache = FALSE, # prevents knitr from caching the results of the chunk.
    fig.width = 7, # Width in inches for plots created in chunk 
    fig.height = 7, # Height in inches for plots created in chunk
    comment = "", # Comment character to preface results with
    tidy = TRUE #Whether to reformat code in a tidy way when displaying it
)

# Import libraries
library(lattice)
library(ggplot2)
library(dplyr) # for pipe operator
library(tidyr) # for tidy dataframe
library(stringr)
```

\pagebreak

# Introduction  
The aim of this document is to get used to the R-Bootcamp exercises and creation of a rmarkdown document.  
__This document is a work in progress__ _and therefore, not checked_  

## Data Manipulation: tidyr
tidyr - dplyr are two pages learned in the R-Bootcamp.

Show data and chunk as follows:
```{r data, include = TRUE, echo = TRUE}
head(diamonds)
```

It is very easy to manipulate data with dplyr. Let's see how to use chaining of data.

```{r, echo = TRUE, include = TRUE}
diamonds$x %>% mean()
# is equivalent to
mean(diamonds$x)
```

### Data frame: dataframe
```{r, echo = TRUE, include = TRUE}
t.num <- 1:10
t.alph <- LETTERS[1:10]
t.logical <- sample(x = c(TRUE, FALSE), size = 10, replace = TRUE)

t <- data.frame(t.num, t.alph, t.logical)
t
```

__TASK:__  
Create a data frame with the following columns:
_columns:_ job, salary, satisfaction, field.exists.since, field.old  

For the following jobs:  
Data Scientist, Banker, Artist, else, gardner

```{r, echo = TRUE, include = TRUE}
d_jobs <- data.frame(
    job = c("Data Scientist", "Banker", "Artist", "else", "gardner")
)

columns <- c("job", "salary", "satisfaction", "field.exists.since", "field.old")

for (column in columns){
    d_jobs[column] <- rep(NA, length(d_jobs$job))
}

d_jobs
```

Now, filter the results and fill-in the values:  
__Salary__  
Data Scientist = \$\$

Banker = \$\$\$    
Artist = \$?    
else = NA    
gardner = \$    

__Satisfaction__    
Data Scientist = Depends  
Banker = Money  
Artist = High  
else = NA  
gardner = Medium  

__field.exists.since__    
Data Scientist = 2015  
Banker = 1000  
Artist = Inf  
else = NA  
gardner = 500  

__field.old__    
Data Scientist = FALSE  
Banker = TRUE  
Artist = TRUE  
else = NA  
gardner = TRUE  

| Author | Date | Version |
|:-------|:-----:|:-------:|
| Bernardo Freire Barboza da Cruz | `r format(Sys.time(), '%d %B, %Y')` | 0.1 |